Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-12 ms.tex
ao figure

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 1.5cm 0 1.5cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed 
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view. 
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}

>>>>

Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO}.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{AO data for all systems imaged. 
The main frame for each single system shows the deep, saturated image.
The inset for each single system shows a shallower, unsaturated image to better
identify companions at close projected orbital separations.
For the two systems with imaged companions, EPIC 201546283 and 201828749,
only unsaturated frames are collected.
All subplots, including insets, are plotted on the same scale.}
\label{fig:AO}
\end{figure*}

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed 
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view. 
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}
